intro

### 2022-03-17 06_Paper/ER-ED/TheoreticalBackground.Rmd
deleted comment
added examples to psychopathology

Psychophysiological measures provide further important information on the effectiveness of emotion regulation strategies (for an overview, see Zaehringer et al.[@Zaehringer2020]).
Compared to cardiovascular, electrodermal, and pupillometric autonomic responses, facial electromyography has been reported consistently across studies to be influenced by emotion regulation with even medium effect sizes.
For example, studies have shown that reappraisal of negative emotion is associated with reduced activity of the corrugator supercilii (associated with anger, sadness, and fear) with _d~-~_ = 0.32 [@Zaehringer2020].
In addition, the levator labii superioris (associated with disgust) has also been associated with reduced activity during reappraisal [@Burr2021]. 
Similar effects have been reported for suppression [@Burr2021], distancing [@Gaertner2021], and distraction [@Schoenfelder2014].
Importantly, results on electromyographic measures  seem to be more consistent compared to other autonomic measures, likely because they are specific to emotional valence and its changes.
<!-- Anne: please add references-->

Similarly to the differences in short term effectiveness, these tactics from three different strategies are also related to different medium and long-term consequences. 
In particular, strategies that do not change the emotional content of the situation, for instance by taking a neutral perspective (i.e., distraction and suppression) are presumed to be disadvantageous in the longer term.
Thus, the self-reported habitual use of suppression is associated with more negative affect and lower general well-being [@GrossJohn2003]. 
In addition, a number of ER strategies <!-- Anne: welche? siehe auch nöchster Kommentar, an irgendeiner Stelle würde ich ein zwei Beispiele nennen.--> have been associated with mental disorders (for meta-analytic review, see Aldao et al. [@Aldao2010]), which led to the postulation of *adaptive* (such as reappraisal, acceptance) and *maladaptive* (such as suppression, rumination) ER strategies.
For example, it was shown that maladaptive ER strategies <!-- Anne: hier würde ich die konkrete Strategie(n) in Klammer nennen--> mediate the effect between neuroticism and depressive symptoms [@Yoon2013].

>>>>

Psychophysiological measures provide further important information on the effectiveness of emotion regulation strategies (for an overview, see Zaehringer et al.[@Zaehringer2020]).
Compared to cardiovascular, electrodermal, and pupillometric autonomic responses, facial electromyography has been reported consistently across studies to be influenced by emotion regulation with even medium effect sizes.
For example, studies have shown that reappraisal of negative emotion is associated with reduced activity of the corrugator supercilii (associated with anger, sadness, and fear) with _d~-~_ = 0.32 [@Zaehringer2020].
In addition, the levator labii superioris (associated with disgust) has also been associated with reduced activity during reappraisal [@Burr2021]. 
Similar effects have been reported for suppression [@Burr2021], distancing [@Gaertner2021], and distraction [@Schoenfelder2014].
Importantly, results on electromyographic measures  seem to be more consistent compared to other autonomic measures, likely because they are specific to emotional valence and its changes.

Similarly to the differences in short term effectiveness, these tactics from three different strategies are also related to different medium and long-term consequences. 
In particular, strategies that do not change the emotional content of the situation, for instance by taking a neutral perspective (i.e., distraction and suppression) are presumed to be disadvantageous in the longer term.
Thus, the self-reported habitual use of suppression is associated with more negative affect and lower general well-being [@GrossJohn2003]. 
In addition, a number of ER strategies, e.g., rumination and suppression, have been associated with mental disorders (for meta-analytic review, see Aldao et al. [@Aldao2010]), which led to the postulation of *adaptive* (such as reappraisal, acceptance) and *maladaptive* (such as suppression, rumination) ER strategies.
For example, it was shown that maladaptive ER strategies <!-- Anne: hier würde ich die konkrete Strategie(n) in Klammer nennen--> mediate the effect between neuroticism and depressive symptoms [@Yoon2013].
